### 2024-03-29 paper/main.tex
Equations almost finalized

\documentclass[12pt,letterpaper]{article}
\usepackage{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage{fontspec} %XeLatex
\usepackage{soul,xcolor}
\usepackage{graphicx,wrapfig}
\usepackage{float}
\usepackage{caption}
\graphicspath{ {./figures/} }
\usepackage[backend=biber]{biblatex}
\usepackage[paper=letterpaper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=0.0in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=1.0in,               % 1 inch margins
            includemp]{geometry}
\usepackage{fontspec} %XeLatex
\setmainfont{AvenirLTProBook.otf}[
    Path =fonts/,
    BoldFont = AvenirNextLTProBold.otf,
    %BoldFont = AvenirLTProHeavy.otf, % another option for bold font
    ItalicFont = AvenirLTProBookOblique.otf,
    BoldItalicFont = AvenirLTProHeavyOblique.otf
]
% Set caption styles
% \DeclareCaptionLabelFormat{table}{1-2}
\captionsetup[table]{labelfont=bf,labelsep=period}
\captionsetup[figure]{labelfont=bf,labelsep=period}

@@

\SectionHeader{Methods}
\begin{table}[h]
    \centering
    \begin{tabular}{|l | c|}
        \hline
        Agent Movement Onset Time Mean        & $\mu_{A}$         \\
        Agent Movement Onset Time Uncertainty & $\sigma_{A}$      \\
        Reaction Time Mean                    & $\mu_{RT}$        \\
        Reaction Time Uncertainty             & $\sigma_{RT}$     \\
        Movement Time Mean                    & $\mu_{MT}$        \\
        Movement Time Uncertainty             & $\sigma_{MT}$     \\
        Neuromechanical Delay Mean            & $\mu_{NMD}$       \\
        Neuromechanical Delay Uncertainty     & $\sigma_{NMD}$    \\
        Stopping Time Uncertainty             & $\sigma_{\tau}$   \\
        Switch Time Mean                      & $\mu_{switch}$    \\
        Switch Time Uncertainty               & $\sigma_{switch}$ \\
        \hline
    \end{tabular}
    \caption[]{Inputs to the model}
\end{table}

\begin{table}[h]
    \centering
    \begin{tabular}{|l | c|}
        \hline
        Reaction Time Delay       & $\mathcal{N}(\mu_{RT},\sigma_{RT})$         \\
        Movement Time Delay       & $\mathcal{N}(\mu_{MT},\sigma_{MT})$         \\
        Neuromechanical Delay     & $\mathcal{N}(\mu_{NMD},\sigma_{NMD})$       \\
        Stopping Time Uncertainty & $\sigma_{\tau}$                             \\
        Switch Time Delay         & $\mathcal{N}(\mu_{switch},\sigma_{switch})$ \\
        Agent Movement Onset Time & $\mathcal{N}(\mu_{A},\sigma_{A})$           \\
        \hline
    \end{tabular}
    \caption[]{Inputs to the model}
\end{table}

% Define pdf and cdf
\begin{equation}
    f(t) = \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{1}{2}(\frac{t-\mu}{\sigma})^2}
\end{equation}
\begin{equation}
    F(t) = P(T\leq t) = \int_{-\infty}^{t} f(t)dt
\end{equation}
\begin{equation}
    t \in [0,1500]
\end{equation}
\begin{equation}
    T\sim\mathcal{N}(\mu,\sigma)
\end{equation}

% Define prob react and guess
\begin{equation}
    P(React|\tau) = P(\tau>\mu_{A}; \sigma_{tau}, \sigma_{A})
\end{equation}
\begin{equation}
    P(Guess|\tau) = P(\tau<\mu_{A}; \sigma_{tau}, \sigma_{A})
\end{equation}

% Define expected value
\begin{equation}
    \mu_{X} = \sum_{i = -\infty}^{\infty}x_{i}f(x_{i};\mu_{X}, \sigma_{X})
\end{equation}

% Define indicator function
\begin{equation}
    \mathbbm{1}_{a_{i},t_{i} \in S} = 
    \begin{cases}
        1, & \text{if } a_{i},t_{i} \in S \\
        0, & \text{if }  a_{i},t_{i} \notin S
    \end{cases}    
\end{equation}

% Define

% Movement Onset times
\begin{equation}
    \mu_{RMO} = \mu_{A_{cutoff}} + \mu_{RT}
\end{equation}
\begin{equation}
    \sigma_{RMO} = \sqrt{\sigma_{A_{cutoff}}^2 + \sigma_{RT}^2}
\end{equation}
\begin{equation}
    \mu_{GMO} = \\tau +  \mu_{NMD} + \mu_{switch}
\end{equation}
\begin{equation}
    \sigma_{GMO} = \sqrt{\sigma_{\tau}^2 + \sigma_{NMD}^2 + \sigma_{switch}^2}
\end{equation}

% Scores

\begin{equation}
    R_{win} = 1
\end{equation}
\begin{equation}
    R_{indecision} = 0
\end{equation}
\begin{equation}
    R_{incorrect} = 0
\end{equation}

>>>>

\documentclass[12pt,letterpaper]{article}
\usepackage{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{bbm}
\usepackage{fontspec} %XeLatex
\usepackage{soul,xcolor}
\usepackage{graphicx,wrapfig}
\usepackage{float}
\usepackage{caption}
\graphicspath{ {./figures/} }
\usepackage[backend=biber]{biblatex}
\usepackage[paper=letterpaper,
            %includefoot, % Uncomment to put page number above margin
            marginparwidth=0.0in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=1.0in,               % 1 inch margins
            includemp]{geometry}
\usepackage{fontspec} %XeLatex
\setmainfont{AvenirLTProBook.otf}[
    Path =fonts/,
    BoldFont = AvenirNextLTProBold.otf,
    %BoldFont = AvenirLTProHeavy.otf, % another option for bold font
    ItalicFont = AvenirLTProBookOblique.otf,
    BoldItalicFont = AvenirLTProHeavyOblique.otf
]
% Set caption styles
% \DeclareCaptionLabelFormat{table}{1-2}
\captionsetup[table]{labelfont=bf,labelsep=period}
% \captionsetup[figure]{labelfont=bf,labelsep=period}

\DeclareMathOperator*{\argmax}{arg\,max} % thin space, limits underneath in displays

@@

\SectionHeader{Methods}
\begin{table}[h]
    \centering
    \begin{tabular}{|l | c|}
        \hline
        Agent Movement Onset Time Mean        & $\mu_{a}$         \\
        Agent Movement Onset Time Uncertainty & $\sigma_{a}$      \\
        Reaction Time Mean                    & $\mu_{rt}$        \\
        Reaction Time Uncertainty             & $\sigma_{rt}$     \\
        Movement Time Mean                    & $\mu_{mt}$        \\
        Movement Time Uncertainty             & $\sigma_{mt}$     \\
        Neuromechanical Delay Mean            & $\mu_{nmd}$       \\
        Neuromechanical Delay Uncertainty     & $\sigma_{nmd}$    \\
        Stopping Time Uncertainty             & $\sigma_{\tau}$   \\
        Switch Time Mean                      & $\mu_{switch}$    \\
        Switch Time Uncertainty               & $\sigma_{switch}$ \\
        \hline
    \end{tabular}
    \caption[]{Inputs to the model}
\end{table}

\begin{table}[h]
    \centering
    \begin{tabular}{|l | c|}
        \hline
        Reaction Time             & $\mathcal{N}(\mu_{rt},\sigma_{rt})$         \\
        Movement Time             & $\mathcal{N}(\mu_{mt},\sigma_{mt})$         \\
        Neuromechanical Delay     & $\mathcal{N}(\mu_{nmd},\sigma_{nmd})$       \\
        Switch Time               & $\mathcal{N}(\mu_{switch},\sigma_{switch})$ \\
        Agent Movement Onset Time & $\mathcal{N}(\mu_{A},\sigma_{A})$           \\
        Stopping Time Uncertainty & $\sigma_{\tau}$                             \\
        \hline
    \end{tabular}
    \caption[]{Inputs to the model}
\end{table}

% Define pdf and cdf
\begin{equation}
    f_{X}(x; \mu, \sigma) = \frac{1}{\sigma\sqrt{2\pi}}e^{-\frac{1}{2}(\frac{x-\mu}{\sigma})^2}
\end{equation}
\begin{equation}
    P(u\leq X\leq v) = \int_{u}^{v} f_{X}(x; \mu, \sigma)dt
\end{equation}
% \begin{equation}
%     t \in [0,1500]
% \end{equation}
\begin{equation}
    X\sim\mathcal{N}(\mu,\sigma)
\end{equation}

% % Define prob react and guess
% \begin{equation}
%     P(React|\tau) = P(\tau>\mu_{A}; \sigma_{\tau}, \sigma_{A})
% \end{equation}
% \begin{equation}
%     P(Guess|\tau) = P(\tau<\mu_{A}; \sigma_{\tau}, \sigma_{A})
% \end{equation}

% Define random variables A and T
% Define expected value
\begin{equation}
    \mu_{A} = \mathbb{E}[A] = \int_{-\infty}^{\infty}a \cdot f_{A}(a)dx
\end{equation}

\begin{align}
    A & \sim\mathcal{N}(\mu_{A},\sigma_{A}) \\
    T & \sim\mathcal{N}(\tau,\sigma_{\tau})
\end{align}

% Define indicator function and the set S
\begin{align}
     & \mathbbm{1}_{a \in S} =
    \begin{cases}
        1, & \text{if } a \in S     \\
        0, & \text{if }  a \notin S
    \end{cases}                                                             \\
     & \text{\emph{where} } S = \{a \mid a < t; \hspace{2pt} a,t \in \mathbb{R}\} \nonumber
\end{align}

% Define Cutoff react mean 
\begin{equation}
    \mu_{A_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} a \cdot p(a) \cdot p(t) \cdot \mathbbm{1}_{a \in S} \ dxdt} {P(A<T) }
\end{equation}

\begin{equation}
    \sigma^2_{A_{react}} = \dfrac{\int_{-\infty}^{\infty}  \int_{-\infty}^{\infty} (a - \mu_{A_{react}})^2 \cdot p(a) \cdot p(t_{j}) \cdot \mathbbm{1}_{a \in S} \ dx \ dt}{P(A<T)}
\end{equation}

% Movement Onset times
\begin{equation}
    \mu_{mo_{react}} = \mu_{A_{react}} + \mu_{rt}
\end{equation}
\begin{equation}
    \sigma_{mo_{react}} = \sqrt{\sigma_{A_{react}}^2 + \sigma_{rt}^2}
\end{equation}
\begin{equation}
    \mu_{mo_{guess}} = \tau +  \mu_{nmd} + \mu_{switch}
\end{equation}
\begin{equation}
    \sigma_{mo_{guess}} = \sqrt{\sigma_{\tau}^2 + \sigma_{nmd}^2 + \sigma_{switch}^2}
\end{equation}

% Scores 
\begin{equation}
    R_{win} = 1
\end{equation}
\begin{equation}
    R_{indecision} = 0
\end{equation}
\begin{equation}
    R_{incorrect} = 0
\end{equation}

% Prob React and Guess
\begin{align}
    P(React)             & = P(A<T) \nonumber                                      \\
                         & = P(A-T<0) \nonumber                                    \\
                         & = P(Z<0)                                                \\
    \text{\emph{where} } & Z\sim \mathcal{N}(\mu_{z}, \sigma_{z})   \nonumber      \\
                         & \mu_z = \mu_A - \mu_\tau                 \nonumber      \\
                         & \sigma_z = \sqrt{\sigma_{A}^2 + \sigma_{T}^2} \nonumber
\end{align}

\begin{align}
    P(G) = 1 - P(React)
\end{align}

% Target Reach Time 
\begin{align}
    \mu_{reach_{react}} =\mu_{mo_{react}} + \mu_{mt}                      \\
    \sigma_{reach_{react}} = \sqrt{\sigma_{mo_{react}}^2 + \sigma_{mt}^2} \\
    \mu_{reach_{guess}} =\mu_{mo_{guess}} + \mu_{mt}                      \\
    \sigma_{reach_{guess}} = \sqrt{\sigma_{mo_{guess}}^2 + \sigma_{mt}^2}
\end{align}

% Probability of Reaching Target
\begin{align}
    P(Reach|React) = P(X_{reach_{react}} < 1500) \\
    \text{\emph{where} } X_{reach_{react}} \sim \mathcal{N}(\mu_{reach_{react}}, \sigma_{reach_{react}}) \nonumber
\end{align}
\begin{align}
    P(Reach|Guess) = P(X_{reach_{guess}} < 1500) \\
    \text{\emph{where} } X_{reach_{guess}} \sim \mathcal{N}(\mu_{reach_{guess}}, \sigma_{reach_{guess}}) \nonumber
\end{align}

% Probability of being correct
\begin{equation}
    P(Correct|React) = 1.0
\end{equation}
\begin{equation}
    P(Correct|Guess) = 0.5
\end{equation}

% Probability of winning sequence
\begin{equation}
    P(Win|React) = P(Reach|React) \cdot P(Correct|React)
\end{equation}
\begin{equation}
    P(Win|Guess) = P(Reach|Guess) \cdot P(Correct|Guess)
\end{equation}
\begin{equation}
    P(Win) = P(React) \cdot P(Win|React) + P(Guess) \cdot P(Win|Guess) 
\end{equation}

% Probability of incorrect sequence 
\begin{equation}
    P(Incorrect|React) = P(Reach|React) \cdot (1 - P(Correct|React))
\end{equation}
\begin{equation}
    P(Incorrect|Guess) = P(Reach|Guess) \cdot (1 - P(Correct|Guess))
\end{equation}
\begin{equation}
    P(Incorrect) = P(React) \cdot P(Incorrect|React) + P(Guess) \cdot P(Incorrect|Guess) 
\end{equation}

% Probability of incorrect sequence 
\begin{equation}
    P(Indecision|React) = 1 - P(Reach|React)
\end{equation}
\begin{equation}
    P(Indecision|Guess) = 1 - P(Reach|Guess)
\end{equation}
\begin{equation}
    P(Indecision) = P(React) \cdot P(Indecision|React) + P(Guess) \cdot P(Indecision|Guess) 
\end{equation}

% Expected Reward
\begin{equation}
    R_{win} = 1
\end{equation}
\begin{equation}
    R_{indecision} = 0
\end{equation}
\begin{equation}
    R_{incorrect} = 0
\end{equation}

\begin{align}
    \mathbb{E}[R] = & P(Win) \cdot R_{Win} + P(Incorrect) \cdot R_{Incorrect} + P(Indecision) \cdot R_{Indecision}
\end{align}

% Maximize expected reward with tau
\begin{equation}
    \tau = \underset{\tau \in [0,2000]}{argmax}(\mathbb{E}[R])
\end{equation}
